### 2015-07-15 thesis/thesis/abstract.tex
changes

In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms. We study the community formation problem in two different settings: 1) Communities with centralized manager having complete information using cooperative game-theoretic techniques 2) Communities with distributed decision making mechanisms having incomplete information using training methods. We propose mechanisms for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities. Then in order to address the coopetitive relation within communities of web services, we propose a decision making mechanism for our web services to efficiently choose competition or cooperation strategies to maximize their payoffs. We prove that the proposed decision mechanism is efficient and can be implemented in time linear in the length of the time period considered for the analysis and the number of services in the community. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real web services dataset.

>>>>

In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms. We study the community formation problem in two different settings: (1) Communities with centralized manager having complete information using cooperative game-theoretic techniques (2) Communities with distributed decision making mechanisms having incomplete information using training methods. We propose mechanisms for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities. Then in order to address the coopetitive relation within communities of web services, we propose a decision making mechanism for our web services to efficiently choose competition or cooperation strategies to maximize their payoffs. We prove that the proposed decision mechanism is efficient and can be implemented in time linear in the length of the time period considered for the analysis and the number of services in the community. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real web services dataset.

### 2015-07-15 thesis/thesis/chap5/chap5.tex
changes

\begin{figure}%[h]
%\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[scale=0.47]{Figures/graphbgtmed.eps}
\includegraphics[scale=0.47]{Figures/graphrep.eps}
\caption{Part (a): Cumulative community budget comparison. Part
(b): Average community reputation comparison over different
strategic decisions.} \label{Graph1}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{Figures/graphtaskdone.eps}
\includegraphics[scale=0.35]{Figures/graphtasksatisfaction.eps}
\includegraphics[scale=0.35]{Figures/graphavgqostask.eps}
\caption{Overall performance from community's point of view. Part
(a) Total number of tasks successfully done. Part (b) Ratio of
tasks satisfied with required QoS. Part (c) Average QoS of
performed tasks.} \label{graph_task}
\end{figure}

@@

\begin{figure}%[h]
%\centering
\includegraphics[scale=0.47]{Figures/graphdev.eps}
\includegraphics[scale=0.47]{Figures/graphdev2.eps}
\caption{Utility loss while deviating from our coopetitive
decision process. Part (a) Overall budget when deviating from our
model in 0, 10, 20, 30, 40, and 50 percent of decisions. Part (b)
Ratio of getting earning utility (budget) when deviating from our
coopetitive strategy in 1 to 10 decisions.} \label{graph_dev}
\end{figure}

@@

Our model has the advantage of being simple and taking into account three important factors: (1) rational services seek better status in the environment by joining the community; (2) rational information service agents obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services while the information service agents challenge for providing truthful information. As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally. Moreover, we would like to achieve a collusion resistant efficiency mechanism, which is still an open problem in open environments.

>>>>

\begin{figure}%[h]
%\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[scale=0.55]{Figures/graphbgtmed.eps}
\includegraphics[scale=0.55]{Figures/graphrep.eps}
\caption{Part (a): Cumulative community budget comparison. Part
(b): Average community reputation comparison over different
strategic decisions.} \label{Graph1}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.55]{Figures/graphtaskdone.eps}
\includegraphics[scale=0.55]{Figures/graphtasksatisfaction.eps}
\includegraphics[scale=0.55]{Figures/graphavgqostask.eps}
\caption{Overall performance from community's point of view. Part
(a) Total number of tasks successfully done. Part (b) Ratio of
tasks satisfied with required QoS. Part (c) Average QoS of
performed tasks.} \label{graph_task}
\end{figure}

@@

\begin{figure}%[h]
%\centering
\includegraphics[scale=0.55]{Figures/graphdev.eps}
\includegraphics[scale=0.55]{Figures/graphdev2.eps}
\caption{Utility loss while deviating from our coopetitive
decision process. Part (a) Overall budget when deviating from our
model in 0, 10, 20, 30, 40, and 50 percent of decisions. Part (b)
Ratio of getting earning utility (budget) when deviating from our
coopetitive strategy in 1 to 10 decisions.} \label{graph_dev}
\end{figure}

@@

Our model has the advantage of being simple and taking into account three important factors: (1) rational web services seek better status in the environment by joining the community; (2) rational web services obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services
%As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally. Moreover, we would like to achieve a collusion resistant efficiency mechanism, which is still an open problem in open environments.

### 2015-07-15 thesis/thesis/chap6/chap6.tex
changes

In this theses we proposed three models for aggregation of web services within communities. The goal of our models are to maximize efficiency by collaborating and forming stable communities. In our first contributions we focused on stability and fairness for all web services within the communities. In this work we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and also fairness and stability of communities. The proposed model offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality. The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.

In our next step of research work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and membership management in communities of web services. In this work we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services. The proposed mechanism helps web services and communities decide with whom to be grouped and cooperate. DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain. In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility. The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature. We performed excrements using real date from 142 users on 4,532 web services during 64 different time slots. The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions. Moreover, the experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our final step of the work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behavior of intelligent services that are active within communities. We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this thesis are also backed by simulation results using a real services dataset. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real services dataset on the web. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits.

@@

As future work, for the community formation in our first model, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal
$\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.

For the distributed model, our future work is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches. In fact, game theory provides powerful techniques for strategic decision making, particularly cooperative and coalition formation games. Hedonic games and fractional hedonic games are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members. We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will stay for long period. The SVM machine learning algorithm is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

@@

%\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi Asl:, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.

@@

%\item H. O. Marey, J. Bentahar, E. Khosrowshahi Asl, M. Mbarki, R. Dssouli, "Agents' Uncertainty in Argumentation-based Negotiation: Classification and Implementation", ANT/SEIT, Hasselt, Belgium, 2014.

%\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.

>>>>

In this theses, we proposed three models for aggregation of web services within communities. The goal of our models are to maximize efficiency by collaborating and forming stable communities. In our first contributions, we focused on stability and fairness for all web services within the communities. In this work we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and also fairness and stability of communities. The proposed model offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality. The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.

In our next step of research work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and membership management in communities of web services. In this work we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services. The proposed mechanism helps web services and communities decide with whom to be grouped and cooperate. DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain. In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility. The ultimate goal of our mechanism is to make a better decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature. We performed excrements using real date from 142 users on 4,532 web services during 64 different time slots. The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions. Moreover, the experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our final step of the work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behavior of intelligent services that are active within communities. We considered two acting strategies where service agents expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this thesis are also backed by simulation results using a real services dataset. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real services dataset on the web. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the less benefits they make.

@@

As future work, for the community formation in our first model, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal
$\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperative game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.

For the distributed model, our future plan is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches. In fact, game theory provides powerful techniques for strategic decision making, particularly cooperative and coalition formation games. Hedonic games and fractional hedonic games are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members. We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will stay for long period. The SVM machine learning algorithm is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

@@

\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi Asl, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.

\item O. Marey, J. Bentahar, E. Khosrowshahi Asl, K. Soltan, R. Dssouli, "Decision making under subjective uncertainty in argumentation-based agent negotiation", Journal of Ambient Intelligence and Humanized Computing, 2015.

@@

\item O. Marey, J. Bentahar, E. Khosrowshahi Asl, M. Mbarki, R. Dssouli, "Agents' Uncertainty in Argumentation-based Negotiation: Classification and Implementation", ANT/SEIT, Hasselt, Belgium, 2014.

\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.
